Reliable Inferences from Simply Parameterised Models

### 2012-08-29 ms.tex
Adding noise
Fake data figure

\section{An Example: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data to explore the properties of simply parameterised models. The
simulated data was generated from the following complex model:
\begin{eqnarray}
\mathcal{M}_0(x) \propto 3\exp\left[-\frac{1}{2}\left(\frac{x}{0.3}\right)^2\right]
+ \exp\left[-\frac{1}{2}\left(\frac{x - 1}{1}\right)^2\right]
+ 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
\end{eqnarray}
The fluxes were evaluated at $x$-values ranging from $-10$ to $10$ in steps
of $0.001$, and then normalised to sum to 1:
\begin{eqnarray}
\sum_{i=1}^N \mathcal{M}_0(x_i) &=& 1.
\end{eqnarray}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{emission_line.eps}
\end{center}
\end{figure*}

>>>>

\section{An Example: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data to explore the properties of simply parameterised models. The
simulated data was generated from the following complex model:
\begin{eqnarray}
\mathcal{M}_0(x) \propto 3\exp\left[-\frac{1}{2}\left(\frac{x}{0.3}\right)^2\right]
+ \exp\left[-\frac{1}{2}\left(\frac{x - 1}{1}\right)^2\right]
+ 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
\end{eqnarray}
The fluxes were evaluated at $x$-values ranging from $-10$ to $10$ in steps
of $0.001$, and then normalised to sum to 1:
\begin{eqnarray}
\sum_{i=1}^N \mathcal{M}_0(x_i) &=& 1.
\end{eqnarray}
To simulate noise in the measurement process, errors $\{\epsilon_i\}$ were added, generated
independently from a normal distribution with mean 0 and standard deviation
$\sigma = 3 \times 10^{-4}$.
This produces noisy data $\mathbf{y} = \{y_1, y_2, ..., y_N\}$:
\begin{eqnarray}
\begin{array}{lccr}
y_i = \mathcal{M}_0(x_i) + \epsilon_i, & & & \epsilon_i \sim \mathcal{N}(0, \sigma^2).
\end{array}
\end{eqnarray}
The simulated data is shown in Figure~\ref{emission_line}.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{emission_line.eps}
\end{center}
\caption{The simulated data that will be used to illustrate the properties of
simply-parameterised models. {\bf Top}: The noise-free true model $\mathcal{M}_0(x)$,
generated from a mixture of three Gaussians, and normalised to a sum of 1.
{\bf Bottom}: Simulated data with added noise.\label{emission_line}}
\end{figure*}

@@
